Classifier Testing

### 2019-05-02 Code/dallin_annotations/09_classifier_testing.Rmd
I cleaned up some comments that didn't seem necessary to me.

### What scripts need to function for this code to work?
##### predict_func.R
* Renamed as 11_predict_func.Rmd in this folder.
* FOUND
* WORKING

##### TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
* FOUND
* NOT WORKING

@@

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R")) # Formerly "R/predict_func.R" in Adriel's original code
source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R")) # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

@@

# Load Models
```{r}
load(here::here("Output", "prcomp4.dat")) # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model(here:here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
# Model50 was built in fasttext_clust_EDA

load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

@@

# Test Classifier
Using this predict() function, we can make predictions about single tweets. All you have to do is type your tweet in the quotations for the second argument. 
```{r}
predict(TweetComplaintPredictor, "")

>>>>

### What scripts need to function for this code to work?
##### predict_func.R
* Renamed as 06_define_prediction_functions.R in this folder.
* FOUND
* WORKING

##### TweetComplaintPredictor.r
* Renamed as 08_define_tweet_complaint_predictor_function.R in this folder.
* FOUND
* NOT WORKING

@@

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)

source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R"))
source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R"))
```

@@

# Load Models
```{r}
load(here::here("Output", "prcomp4.dat"))
fasttextModel <- load_model(here::here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
load(here::here("Output", "xgb.modelPC4.dat"))

TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, "PC4")
```

# Test Classifier
Using this predict() function, we can make predictions about single tweets. All you have to do is type your tweet in the quotations for the second argument. 
```{r}
predict(TweetComplaintPredictor, "Hey why do dogs bark at mailmen?")

@@

Dallin: practicing with the new model
```{r}
train %>% 
  head(10)
